Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-05-07 thesis/paper.tex
case descr

\section{Case Company Description} \label{case_company_description}
The case company is a medium-sized company in the domain of security cameras. The company has its headquarters in Lund, Sweden, but it operates worldwide. The company is the global market leader in the markets of network cameras and video encoders. The company develops embedded software for the security cameras and some of their products are designed to be accessible through APIs that are also developed by the company.

%Try to get information about the users of the API. Either through Imed, or through the interviews.

@@

%Try to motivate why other sampling methods weren't used.

%Info from the interview, add to this section
Has been released, in the form we looked at (supports that we’re doing a ``real'' case study)
They have partners which develop applications using their API. These applications are then used by the end-users of the camera.

%%
Hardware
The API platform is developed for many different types of cameras. 
Some have audio, some don’t, for example.

%%Does this paragraph below belong here or somewhere else? Feels a bit odd!    W: Case Company Description I think
The API itself consisted of two major versions; 1.4 and 2.0. There were no intermediate versions between 1.4 and 2.0. Version 1.4 was actually the same version as 1.0, just with added build options for other hardware platforms. The changes therefore come from the changes between the two major versions. Given that there was an apparent ``big bang'' implementation of the new API, we have tried to determine what existed in the previous version, what was re-implemented and what is brand new.

>>>>

\section{Case Company Description} \label{case_company_description}
The case company is a company operating in the domain of video surveillance. The company has its headquarters in Lund, Sweden with offices in 49 countries worldwide. The company is the global market leader in the markets of network cameras and video encoders. The develops embedded software for the security cameras. The cameras are designed to be accessible through APIs that are developed and maintained by the company.

The API analysed in this study has been deployed for several years. It was recently updated from version 1.4 to version 2.0, which is the current active version. The changes between these two versions is what has been analysed in this study. Between the release of 1.0 and 1.4, no functionality was added, as it only added additional build options for other hardware platforms. The API is used by company partners, which are companies who develop applications for the cameras. These applications are, in turn, used by the end-users of the cameras. The API is developed for a wide range of camera types that offer different functionality and are used for different purposes.

@@
